### 2020-02-10 vesicle_code/docs/permeableVes/main.tex
starting rebuttal forms for adhesion paper
worked on Figure 12 (left)
commenting shuwang code

\section{Problem formulation} \label{sc:formulate}
Consider a semi-permeable vesicle suspended in an unbounded viscous
fluid domain, subjected to an imposed flow $\mbu_\infty(\mbx)$, for any
$\mbx \in \RR^2$.  Assume that the interior and exterior fluids have the same viscosity $\mu$. Let $\mbx$ be the position of the interface $\gamma$, $\mbu$ the fluid velocity and $p$ the pressure. In the vanishing Reynolds number limit, the governing equations for the ambient fluid can be written as: 
%
\begin{subequations}
\begin{align}
-\nabla p + \mu \triangle \mbu = 0 \quad\text{in}\quad
  \RR^2\setminus\gamma  &  \\
% 
\nabla \cdot \mbu = 0  \quad\text{in}\quad \RR^2\setminus\gamma &\\
%
\mbu(\mbx) \rightarrow \mbu_\infty(\mbx) \quad \text{as} \quad  \norm{\mbx} \rightarrow \infty & 
 \end{align} \label{eqn:governing}
\end{subequations}%
%
The modified jump conditions in the case of a semi-permeable vesicle can be summarized as follows.  Let $\mbn$ the outward normal to $\gamma$ and $\jump{\cdot}$ denote the jump across the interface. The jump condition for the hydrodynamic stress remains the same:
%
%Then, define
%\beq \mbf_i = \lim_{\mbx \rightarrow \gamma^-} \sigma (\mbx)\cdot\mbn,  \eeq
%\beq \mbf_e =  \lim_{\mbx \rightarrow \gamma^+} \sigma (\mbx)\cdot\mbn, \eeq
%\beq \jump{\mbv\cdot \mbt} = 0 \eeq
%\beq \jump{\mbv\cdot\mbn} = \beta (\mbf_i + \mbf_e)\cdot\mbn \eeq
\beq \jump{\Sigma\cdot\mbn} = \mbf_\text{mem}, \eeq
where $\Sigma$ is the hydrodynamic stress tensor. The fluid velocity is continuous across the membrane i.e.,
\beq \jump{\mbu} = 0. \eeq
However, the kinematic condition is modified to account for the fact that the fluid can move through the membrane. A standard choice appears to be
%
\beq \mbu - \dot{\mbx} = - \beta (\mbf_\text{mem} \cdot \mbn) \mbn \quad\text{on}\quad\gamma. \eeq
%
Here, $\beta$ is a constant and the membrane force is the usual tension + bending.

@@

>>>>

\section{Problem formulation} \label{sc:formulate}
Consider a semi-permeable vesicle suspended in an unbounded viscous
fluid domain, subjected to an imposed flow $\mbu_\infty(\mbx)$, for any
$\mbx \in \RR^2$.  Assume that the interior and exterior fluids have the same viscosity $\mu$. Let $\mbx$ be the position of the interface $\gamma$, $\mbu$ the fluid velocity and $p$ the pressure. In the vanishing Reynolds number limit, the governing equations for the ambient fluid can be written as: 
%
\begin{subequations}
\begin{align}
-\nabla p + \mu \triangle \mbu = 0 \quad\text{in}\quad
  \RR^2\setminus\gamma  &  \\
% 
\nabla \cdot \mbu = 0  \quad\text{in}\quad \RR^2\setminus\gamma &\\
%
\mbu(\mbx) \rightarrow \mbu_\infty(\mbx) \quad \text{as} \quad  \norm{\mbx} \rightarrow \infty & 
 \end{align} \label{eqn:governing}
\end{subequations}%
%
The modified jump conditions in the case of a semi-permeable vesicle can be summarized as follows.  Let $\mbn$ the outward normal to $\gamma$ and $\jump{\cdot}$ denote the jump across the interface. The jump condition for the hydrodynamic stress remains the same:
\beq \jump{\Sigma\cdot\mbn} = \mbf_\text{mem}, \eeq
where $\Sigma$ is the hydrodynamic stress tensor. The fluid velocity is continuous across the membrane i.e.,
\beq \jump{\mbu} = 0. \eeq
However, the kinematic condition is modified to account for the fact that the fluid can move through the membrane. A standard choice appears to be
%
\beq \mbu - \dot{\mbx} = - \beta (\mbf_\text{mem} \cdot \mbn) \mbn \quad\text{on}\quad\gamma. \eeq
%
Here, $\beta$ is a constant and the membrane force is the usual tension + bending.

%%%%%%%%%%%%%%
\section{{$\Theta-L$} formulation}
Here, we attempt to apply the formulation described by Sohn et
al.~\cite{soh-tse-li-voi-low2010} to a semi-permeable vesicle.  In the
semi-permeable formulation, the vesicle velocity is
\begin{align}
  \pderiv{\XX}{t} = \mbu(\XX(t)) + \beta (\mbf \cdot \mbn) \mbn.
\end{align}
In the {$\Theta-L$} variables, we require a normal velocity $V$, and a
tangential velocity $T$. Since the inextensibility condition is $T_s +
\kappa V = 0$, a condition for the vesicle velocity is
\begin{align}
  (\mbu \cdot \mbs)_s = -\kappa(\beta (\mbf \cdot \mbn) + 
      \mbu \cdot \mbn).
\end{align}
This equation can be solved following equations (32)--(39)
in~\cite{soh-tse-li-voi-low2010}, with the only difference being that
$\tilde{\mbu}$ satisfies
\begin{align}
  (\tilde{\mbu} \cdot \mbs)_s + \kappa(\tilde{\mbu} \cdot \mbn) =
    -(\mbv \cdot \mbs)_s - \kappa(\mbv \cdot \mbn) 
    - \beta\kappa(\mbf \cdot \mbn).
\end{align}
Compared to equation (40), only the last term is new.

@@

\section{Area of a Vesicle}
The area inside a single vesicle $\gamma$ parameterized with $\mbx$ is
\begin{align}
  A(t) = \int_{\gamma} (\mbx \cdot \mbn)\, ds = 
    \int_{0}^{2\pi} \left(\mbx \cdot \pderiv{\mbx}{\theta}^\perp\right)
    \, d\theta.
\end{align}
Taking the time derivative of $A(t)$,
\begin{align}
  \dot{A}(t) &= \int_{0}^{2\pi} \left(
    \dot{\mbx} \cdot \pderiv{\mbx}{\theta}^{\perp} + 
    \mbx \cdot \pderiv{\dot{\mbx}}{\theta}^{\perp}\right) \\
    \, d\theta.
  &= \int_{0}^{2\pi} \left(
    (\dot{\mbx} \cdot \mbn)\|\mbx'(\theta)\| \right) d\theta +
     \int_{0}^{2\pi}
    \mbx \cdot \frac{d}{dt}\left(\mbn |\frac{d\mbx}{d\theta}| \right)
\end{align}

### 2020-02-10 vesicle_code/docs/softmatter/permeableVes.tex
commenting shuwang code

\input my_macros2.tex	
\begin{document}

@@

\subsection{Content permeability rate}

>>>>

\input my_macros2.tex	
\usepackage{todonotes}
\begin{document}

@@

\subsection{Relaxation flow}
We start by considering a single semi-permeable vesicle suspended in a
quiescent Stokes flow. In Figure~\ref{fig:relaxationSnapshots}, we plot
the vesicle configuration at \todo{some number} times. We observe that
the vesicle inflates towards a circular shape.

\begin{figure}[htp]
%  \includegrahpics[width=0.3\textwidth]{figures/relaxationTime1.pdf}
%  \includegrahpics[width=0.3\textwidth]{figures/relaxationTime2.pdf}
%  \includegrahpics[width=0.3\textwidth]{figures/relaxationTime3.pdf}
  \caption{\label{fig:relaxationSnapshots} Snapshots of a single vesicle
  in a relaxation flow. The color on the vesicle is the fluid flux.
  Since the flux is always positive/negative, the vesicle inflates to a
  circle.}
\end{figure}

We next investigate the effect of
